### 2019-08-20 manuscript/manuscript.tex
figure 1 added, some ms text
some new ms words I like

@@

For $t=1$,

\begin{align}
  \var(\widetilde{p}_1 - \widetilde{p}_0) &= \widetilde{p}_1(1-\widetilde{p}_1)\frac{d_1 + n_1 - 1}{(n_1-1)(d_1-1)} + 
 \widetilde{p}_0(1-\widetilde{p}_0)\frac{d_0 + n_0 - 1}{(n_0-1)(d_0-1)} + \\ & \nonumber\;\;\;\;\;\;
\end{align}

\begin{align}
  \widehat{V_t} = \frac{1}{L} \sum_{l=1}^L (\Delta \widetilde{p}_{t,l})^2
\end{align}

TODO

@@

>>>>

Explain G.

We first analyzed \textcite{Barghi2019-qy}, an evolve-and-resequence study with
ten replicate populations exposed to a high temperature environment and evolved
for 60 generations, and sequenced every ten generations. Using the seven
timepoints and ten replicate populations, we estimated a bias-corrected $60
\times 60$ temporal-replicate variance-covariance matrix (see XXX for details).
Since each replicate population was sequenced every ten generations, the
timepoints $t_0 = 0$ generations, $t_1 = 10$ generations, $t_2 = 20$
generations, etc., lead to observed allele frequency changes across ten
generation chunks, $\Delta p_{t_0}, \Delta p_{t_1}, \ldots, \Delta p_{t_6}$.
Consequently, the ten temporal covariance matrices for each of the ten
replicate populations have off-diagonal elements of the form $\cov(\Delta
p_{t_0}, \Delta p_{t_1}) = \cov(p_{t_1} - p_{t_0}, p_{t_2} - p_{t_1}) =
\sum_{i=0}^{10} \sum_{j=10}^{20} \cov(\Delta p_i, \Delta p_j)$. Each diagonal
element has the form $\var(\Delta p_{t_0}) = \sum_{i=0}^{t_0} \var(\Delta
p_{i}) + \sum_{i \ne j}^{t_0} \cov(\Delta p_{i}, \Delta p_{j})$, and is thus a
combination of the effects of drift and selection, as both the variance in
allele frequency changes and cumulative temporal autocovariances terms increase
the variance in allele frequency. With sampling each generation, one could more
accurately partition the total variance in allele frequency change
\parencite{Buffalo2019-io}; while we cannot directly estimate the contribution
of linked selection to the variance in allele frequency change here, the
presence of a positive observed covariance between allele frequency change can
only be caused linked selection.

Averaging across replicate populations, we find positive temporal covariances
that are statistically significant (p < XXX) consistent with linked selection
acting to affect allele frequency changes over very short time periods. We
visualize these covariances in Figure \label{figure-1} (A), which depicts the
temporal covariances through time, for each of the five rows covariance matrix.
Each row represents the temporal covariance $\cov(\Delta p_s, \Delta p_t)$,
between some initial reference generation $s$ (the row of the matrix), and some
later timepoint $t$ (the column of the matrix). For each row, the covariances
at first are positive, and then decay towards zero as expected when directional
selection affects linked variants' frequency trajectories until ultimately
linkage disequilibrium and additive genetic variance for decay
\parencite{Buffalo2019-io}.

we can calculate the temporal
covariances between an initial starting reference generation ($s = \{0, 10, 20,
\ldots, 50\})$.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-1.pdf}
  \caption{$B=5000$ bootstraps, with 100}
  \label{fig:figure-1}
\end{figure}

@@

@@

\subsection{Variance-Covariance Matrix Correction}

With frequency collected at $\tau$ timepoints across $R$ replicate populations
at $L$ loci, we have an $R \times \tau \times L$ array $\mathbf{F}$ of allele
frequencies and $\mathbf{D}$ array of sequencing depths. We calculate the

change the
dimensionality of

\subsection{Block Bootstrap Procedure}
\label{supp:block-bootstrap}
